Growth model analysis

### 2018-03-29 manuscriptAnalysis/MS_Analysis.Rmd
switch to spp-specific abundances

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1517846073_bkt1997_Nimble.RData")

@@

load("D:/projects/linkedModels/data/out/dG_1517850064_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1517853143_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

@@

ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
  geom_freqpoly(binwidth=0.05) +
  geom_freqpoly(aes(int),color = 'brown', data = grInt[['bnt']]) +
  geom_freqpoly(aes(int),color = 'lightblue', data = grInt[['ats']]) +
  xlim(-0.5,1.5) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)

@@

ggplot( sigmaInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
  geom_freqpoly() +
  geom_freqpoly(aes(int),color = 'brown', data = sigmaInt[['bnt']]) +
  geom_freqpoly(aes(int),color = 'lightblue', data = sigmaInt[['ats']]) +
  xlim(-4.5,-1) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)

>>>>

mcmc <- list()
load("D:/projects/linkedModels/data/out/dG_1518555667_bkt1997_Nimble.RData")

@@

load("D:/projects/linkedModels/data/out/dG_1518559325_bnt1997_Nimble.RData")
mcmc[['bnt']]  <- mcmcProcessed

load("D:/projects/linkedModels/data/out/dG_1518559991_ats1997_Nimble.RData")
mcmc[['ats']]  <- mcmcProcessed

@@

ggplot( grInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(exp(int))) +
  geom_freqpoly() +
  geom_freqpoly(aes(exp(int)),color = 'brown', data = grInt[['bnt']]) +
  geom_freqpoly(aes(exp(int)),color = 'lightblue', data = grInt[['ats']]) +
 # xlim(-0.5,1.5) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)

@@

bw <- 0.05
ggplot( sigmaInt[['bkt']] %>% filter(river %in% c('west brook','wb jimmy')), aes(int)) +
  geom_freqpoly(binwidth = bw) +
  geom_freqpoly(aes(int),binwidth = bw,color = 'brown', data = sigmaInt[['bnt']]) +
  geom_freqpoly(aes(int),binwidth = bw,color = 'lightblue', data = sigmaInt[['ats']]) +
  #xlim(-4.5,-1) +
  xlim(-5,2.5) +
  theme_publication() +
  facet_grid(season ~ river + isYOY)
